Circumnuclear Media and Accretion Rates of Quiescent Supermassive Black Holes

### 2015-02-21 ms.tex
working3

To within a constant of order unity, equation (\ref{eq:cooling2}) also equals the ratio of the gas cooling timescale $t_{\rm cool} \equiv (3n kT/2)/\dot{q}_{\rm rad}$ to the free-fall time $t_{\rm ff}$ at the stagnation radius, as can be derived using the equality 
\begin{align}
\rho|_{r_{\rm s}}=\frac{3 q\tff|_{r_{\rm s}}}{2-\Gamma}.
\label{eq:rhors2}
\end{align}
that results by combining equations (\ref{eq:Tanalytic}), \eqref{eq:mdot_analytic}, and~\eqref{eq:mdot_gas}.  \citet{McCourt+12} have argued that cooling instability develops in a hydrostatic atmosphere if $t_{\rm cool} \ll t_{\rm ff}$.

@@

The results of our numerical calculations are uses to study the range of plausible CNM properties and to assess the validity of the analytic expressions provided in the previous section.  Our results are summarized in Table \ref{table:models} and Figure XXX.  Cases for which $(\dot{q}_{\rm heat}/|\dot{q}_{\rm rad}|)_{r_{\rm s}} < 1$ are marked as `thermally unstable', as are cases for which the stagnation radius become very large and could not be resolved, resulting in their calculations being terminated.

>>>>

To within a constant of order unity, equation (\ref{eq:cooling2}) also equals the ratio of the gas cooling timescale $t_{\rm cool} \equiv (3n kT/2)/\dot{q}_{\rm rad}$ to the free-fall time $t_{\rm ff}$ at the stagnation radius, as can be derived using the equality 
\begin{align}
\rho|_{r_{\rm s}}=\frac{3 q\tff|_{r_{\rm s}}}{2-\Gamma}.
\label{eq:rhors2}
\end{align}
that results by combining equations (\ref{eq:Tanalytic}), \eqref{eq:mdot_analytic}, and~\eqref{eq:mdot_gas}.  \citet{McCourt+12} argue cooling instability develops in a hydrostatic atmosphere if $t_{\rm cool} \ll t_{\rm ff}$, so equation (\ref{eq:cooling2}) represents a good proxy for instability in this case as well.

@@

Our numerical results, summarized in Table \ref{table:models} and Figure XXX, allow us to study a range of CNM properties and to assess the validity of the analytic estimates from the previous section.  Cases for which $(\dot{q}_{\rm heat}/|\dot{q}_{\rm rad}|)< 1$ at the stagnation radius are marked as `thermally unstable', as are cases for which the stagnation radius diverges and hence could not be resolved, resulting in their calculations being terminated.
